MC-based feasibility study of new sampling calorimeter for measuring the $\gamma$ incident angle

### 2022-01-04 paper.tex
updates

The angular resolution weakly depends on the width of the strips up to 15 mm and becomes worse with the increasing width. It is found that the incident angle is reconstructed with the compatible angular resolution using front 5 radiation length of the detector. The resolution does not depend on the incident angle up to 30 degrees, and largely depends on the incident energy, which can be expressed as 0.1+1.2$/ \sqrt{E_\gamma}$.

@@

Since the EM shower is evolving via stochastic processes, the incident angle would be reconstructed with a certain angular resolution. Energy deposits from random processes are used to reconstruct the incident angle with the machine learning, which provides better angular resolution. The evolution of the EM shower is generated with the GEANT4 and $\XGB$ was used to reconstruct the incident angle.

The sec~\ref{sec:ems} sec~\ref{sec:res} sec~\ref{sec:sum}
In the following section, the configuration of detector and Monte Carlo simulation for electromagnetic shower generation will be given. In the section III, we will describe how to reconstruct incident angle from the generated detector response by using one of the most attractive toolkit of the machine learning; $\XGB$. Finally, we will summarize our study briefly.

>>>>

The angular resolution weakly depends on the width of the strips up to 15 mm and becomes worse with the increasing width. It is found that the incident angle is reconstructed with the compatible angular resolution using front 5 radiation length (5$X_{0}$) of the detector. The resolution does not depend on the incident angle up to 30 degrees, and largely depends on the incident energy, which can be expressed as 0.1+1.2$/ \sqrt{E_\gamma}$.

@@

Since the EM shower is evolving via stochastic processes, the incident angle would be reconstructed with a certain angular resolution. Energy deposits from random processes are used to reconstruct the incident angle with the machine learning, which provides better angular resolution. The evolution of the EM shower is generated with the GEANT4, and $\XGB$ was used to reconstruct the incident angle.

In sec~\ref{sec:ems}, generic explanation of the EM shower and its evolution. We describe the reconstruction and angular resolution of the sampling calorimeter in sec~\ref{sec:res}. We summarize the study in sec~\ref{sec:sum}.
